---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Needed libraries
```{r}
    library(plyr)
    library(ggplot2)
```
## Loading and preprocessing the data
```{r}
      unzip("activity.zip")
      data<-read.csv("activity.csv",sep = ",")
      data$date <- as.Date(data$date, "%Y-%m-%d")
      
```

## What is mean total number of steps taken per day?`
### Calculate the total number of steps taken by day
```{r}
      stepSumByDate <- ddply(data, .(date), summarise, sumSteps = sum(steps, na.rm = TRUE))
      ggplot(stepSumByDate, aes(date, sumSteps))+ ggtitle("Sum steps by date")+theme(plot.title = element_text(face="bold"))+geom_histogram(stat = "identity")
```
### Calculate and report the mean and median of the total number of steps per day
```{r}
      stepMeanByDate <- ddply(data, .(date), summarise, meanSteps = mean(steps, na.rm = TRUE))
      #ggplot(stepMeanByDate, aes(date, meanSteps))+ ggtitle("Steps by date")+theme(plot.title = element_text(face="bold"))+geom_line()

      stepMedianByDate <- ddply(data, .(date), summarise, medianSteps = median(steps, na.rm = TRUE ))
    #ggplot(stepMedianByDate, aes(date, medianSteps))+ ggtitle("Steps by date")+theme(plot.title = element_text(face="bold"))+geom_line()
      #Merge and melt the mean and median to plt them together
      aux<-merge(stepMeanByDate,stepMedianByDate,by="date")

      #Melt (write Mean values below median values)
      meltedData <- melt(aux, id="date") 

      ggplot(data=meltedData,aes(x=date, y=value, colour=variable))+ggtitle("Steps by date")+theme(plot.title = element_text(face="bold"))+geom_line()
      ggplot(data=meltedData,aes(x=date, y=value, colour=variable))+ggtitle("Steps by date")+theme(plot.title = element_text(face="bold"))+geom_line()
      
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
