---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Needed libraries
```{r}
    library(plyr)
    library(ggplot2)
    library("reshape2")
```
## Loading and preprocessing the data
```{r}
      unzip("activity.zip")
      data<-read.csv("activity.csv",sep = ",")
      data$date <- as.Date(data$date, "%Y-%m-%d")
      
```

## What is mean total number of steps taken per day?`
### Calculate the total number of steps taken by day
```{r}
      stepSumByDate <- ddply(data, .(date), summarise, sumSteps = sum(steps, na.rm = TRUE))
      ggplot(stepSumByDate, aes(date, sumSteps))+ ggtitle("Sum steps by date")+theme(plot.title = element_text(face="bold"))+geom_histogram(stat = "identity")
```
### Calculate and report the mean and median of the total number of steps of the whole period
```{r}
      totalStepMean <- mean(stepSumByDate$sumSteps,na.rm = TRUE)

      totalStepMedian <- median(stepSumByDate$sumSteps,na.rm = TRUE)
      
```

## What is the average daily activity pattern?



## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
