```{r package_options, include=FALSE}
knitr::opts_knit$set(progress = TRUE, verbose = TRUE)
```
---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Needed libraries
```{r}
    library(plyr)
    library(ggplot2)
    library("reshape2")
```
## Loading and preprocessing the data
```{r}
      unzip("activity.zip")
      data<-read.csv("activity.csv",sep = ",")
      data$date <- as.Date(data$date, "%Y-%m-%d")
      
```

## What is mean total number of steps taken per day?`

  1. **Calculate the total number of steps taken per day**
```{r}
      stepSumByDate <- ddply(data, .(date), summarise, sumSteps = sum(steps, na.rm = TRUE))
      ggplot(stepSumByDate, aes(date, sumSteps))+ ggtitle("Sum steps by date")+theme(plot.title = element_text(face="bold"))+geom_histogram(stat = "identity",colour="black",fill="red")

```
  2. **Calculate and report the mean and median of the total number of steps taken per day**
```{r}

      mean(stepSumByDate$sumSteps,na.rm = TRUE)
 
      median(stepSumByDate$sumSteps,na.rm = TRUE)

```


## What is the average daily activity pattern?

   1. **Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)**
```{r}
      stepMeanByInterval <- ddply(data, .(interval), summarise, meanSteps = mean(steps, na.rm = TRUE))
      ggplot(stepMeanByInterval, aes(interval,meanSteps))+ ggtitle("Avg. Steps by day interval")+theme(plot.title = element_text(face="bold"),axis.text.x = element_text(angle = 45, hjust = 1))+scale_x_continuous(breaks=seq(0, 3000, by=100))+geom_line()
```


   2. **Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?**
   
```{r}
   
       stepMeanByInterval[which.max(stepMeanByInterval$meanSteps),]
   
```
   
## Imputing missing values

1.**Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)**
```{r}
      length(is.na(data$steps))
```

2. **Devise a strategy for filling in all of the missing values in the dataset.**
     I will replace the NA for the mean of the given interval

```{r}
#Create a function to replace na by the result of the function fun over the non missing values
     funcToApply <- function(x, fun) {
                  missing <- is.na(x)
                  replace(x, missing, fun(x[!missing]))
    }

#use the ddply to apply the function 
    data2<-ddply(data, ~ interval, transform, steps = funcToApply(steps, mean))

#reorder the data by date
      dataNoNa<-data2[order(as.Date(data2$date,format("%Y-%m-%d"))),]

      stepSumByDateNoNa <- ddply(dataNoNa, .(date), summarise, sumSteps = sum(steps, na.rm = TRUE))
      ggplot(stepSumByDateNoNa, aes(date, sumSteps))+ ggtitle("Sum steps by date (NA replaced by the interval mean)")+theme(plot.title = element_text(face="bold"))+geom_histogram(stat = "identity",colour="black",fill="red")
```

## Are there differences in activity patterns between weekdays and weekends?
